Model LF

### 2022-10-30 Final test.Rmd
Commit

## New equations

```{r}
yk_l_ds = prodk_ds * LF
ur_ds = 1- (yk_ds/yk_l_ds)# skifted

@@

COMMENT> 
IDENTITY> yk_l_ds
EQ> yk_l_ds = prodk_ds * lf

COMMENT> 
IDENTITY> ur_ds
EQ> ur_ds = 1- (yk_ds/yk_l_ds)

@@

COMMENT> 
IDENTITY> ur
EQ> ur = ur_ds +alpha_140 + alpha_141*SD1 + alpha_142*SD2 + alpha_143*SD3 - mean_ur

@@

S_modelData$ur_test = unemp/LF

>>>>

@@

COMMENT> 
IDENTITY> ur
EQ> ur = unemp/lf

COMMENT> 
IDENTITY> ur_ds
EQ> ur_ds = ur -(alpha_140 + alpha_141*SD1 + alpha_142*SD2 + alpha_143*SD3) + mean_ur

@@

@@

S_modelData$ur = ur
